Matching Bullets

### 2015-12-08 imaging-paper.Rnw
land 5 not land 1 of bullet 1

\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_fit} Loess fit for land 1 of bullet 1.}
<<loess_fit, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE,  message=FALSE>>=

@@

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess$resid + ylab("Residual of Loess Fit")
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 5 of bullet 1 (Barrel 1).}
\end{figure}

@@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch-rgl}\hh{Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

>>>>

\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_fit} Loess fit for land 5 of bullet 1.}
<<loess_fit, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE,  message=FALSE>>=

@@

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 5 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess$resid + ylab("Residual of Loess Fit")
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 5 of bullet 1 (Barrel 1).}
\end{figure}

@@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land 5 of bullet 1 and land 1 of bullet 2.}}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch-rgl}\hh{Different view of the manually adjusted side-by-side comparison of land 5 of bullet 1 and land 1 of bullet 2.}}
\end{figure}
